#Getting Ready

```{r}
library(knitr)
opts_chunk$set(echo = TRUE)
library(dplyr)
library(lubridate)
library(ggplot2)
```

#Loading the Data

```{r}
data <- read.csv("/Users/richkonar/activity.csv", header = TRUE, sep = ',', colClasses = c("numeric", "character", "integer"))
```

#Tidying Data

```{r}
data$date <- ymd(data$date)
str(data)
head(data)
```

#What is the mean total number of steps taken each day?

```{r}
steps <- data %>%
  filter(!is.na(steps)) %>%
  group_by(date) %>%
  summarize(steps = sum(steps)) %>%
  print
```

#Making the Histogram
```{r}
ggplot(steps, aes(x = steps)) +
  geom_histogram(fill = "dodgerblue4", binwidth = 1000) +
  labs(title = "Histogram of Steps per day", x = "Steps per day", y = "Frequency")
```

##Mean Steps

```{r}
mean_steps <- mean(steps$steps, na.rm = TRUE)
median_steps <- median(steps$steps, na.rm = TRUE)
```

```{r}
mean_steps
```

```{r}
median_steps
```

#What is the average daily activity pattern?

```{r}
interval <- data %>%
  filter(!is.na(steps)) %>%
  group_by(interval) %>%
  summarize(steps = mean(steps))
```

#Making the Plot

```{r}
ggplot(interval, aes(x=interval, y=steps)) + geom_line(color = "dodgerblue4")
```

##Max steps on average across all days

```{r}
interval[which.max(interval$steps),]
```

#Imputing missing values

```{r}
sum(is.na(data$steps))
```

```{r}
data_full <- data
nas <- is.na(data_full$steps)
avg_interval <- tapply(data_full$steps, data_full$interval, mean, na.rm=TRUE, simplify=TRUE)
data_full$steps[nas] <- avg_interval[as.character(data_full$interval[nas])]
```

```{r}
sum(is.na(data_full$steps))
```

```{r}
steps_full <- data_full %>%
  filter(!is.na(steps)) %>%
  group_by(date) %>%
  summarize(steps = sum(steps)) %>%
  print
```

#Making the Plot 3

```{r}
ggplot(steps_full, aes(x = steps)) +
  geom_histogram(fill = "dodgerblue4", binwidth = 1000) +
  labs(title = "Histogram of Steps per day, including missing values", x = "Steps per day", y = "Frequency")
```

##What's the mean & median?

```{r}
mean_steps_full <- mean(steps_full$steps, na.rm = TRUE)
median_steps_full <- median(steps_full$steps, na.rm = TRUE)
```

```{r}
mean_steps_full
```

```{r}
median_steps_full
```

#Are there differences in activity patterns between weekdays and weekends?

```{r}
data_full <- mutate(data_full, weektype = ifelse(weekdays(data_full$date) == "Saturday" | weekdays(data_full$date) == "Sunday", "weekend", "weekday"))
data_full$weektype <- as.factor(data_full$weektype)
head(data_full)
```

#Making the Plot 4

```{r}
interval_full <- data_full %>%
  group_by(interval, weektype) %>%
  summarise(steps = mean(steps))
s <- ggplot(interval_full, aes(x=interval, y=steps, color = weektype)) +
  geom_line() +
  facet_wrap(~weektype, ncol = 1, nrow=2)
print(s)
```
